### 2013-10-14 article.tex
Added preliminary results.

% CONTRIBUTION - RESULTS
\subsection{Results}
\label{sec:contribution:results}

@@

% CONCLUSION
\section{Conclusion}
\label{sec:conclusion}
% Summary
%	Vilken bakgrund, utmaning, ansats och resultat omfattar studien?
% Discussion
%	Vilka relaterade studier förhåller sig materialet till?
%	Vilka tvetydliga aspekter av studien kräver diskussion?
% Answer and Oppertunity
%	Vilka fortsatta studier föreslår rapportens författare?

>>>>

% CONTRIBUTION - RESULTS
\subsection{Results}
\label{sec:contribution:results}
Preliminary results indicate a surprisingly well-performing WARP, roughly only doubling the execution time in regards to the same kernel hardware accelerated. Each configuration has been has been run using the same integer-precision 200x200-matrix. To gather the results presented below, each scenario has been run 100 times each. Please observe that these are preliminary tests, and more data is to be gathered before the closing of this article. \\
The results gathered during preliminary testing are presented below:
\begin{center}
	\begin{tabular}{| l | l | l | l |}
	\hline
	Acceleration & Min (ms) & Max (ms) & Average (ms)	\\ \hline
	Hardware & 25.86  & 43.12  & 26.41			\\ \hline
	Software & 16141.6 & 16906.7 & 16390.6		\\ \hline
	WARP & 46.18 & 64.25 & 48.47				\\
	\hline
	\end{tabular}
\end{center}

@@

% CONCLUSION
\section{Conclusion}
\label{sec:conclusion}
Conclusion left out in regards to further development and analysis.
% Summary
%	Vilken bakgrund, utmaning, ansats och resultat omfattar studien?
% Discussion
%	Vilka relaterade studier förhåller sig materialet till?
%	Vilka tvetydliga aspekter av studien kräver diskussion?
% Answer and Oppertunity
%	Vilka fortsatta studier föreslår rapportens författare?
